The Bug Catalog of the Maven Repository Ecosystem

### 2014-01-19 docs/msr.tex
adding content, minor structure changes

\section{Introduction}
\label{sec:intro}
Intorduction.

@@

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.35]{figures/bug_percent}
	\caption{Bug percentage in Maven repository.}
	\label{fig:bug-per} 
\end{figure}

@@

\bibliographystyle{abbrv}
\bibliography{evol}  
\end{document}

>>>>

\section{Introduction}
\label{sec:intro}

In this paper we present a dataset produced after
analyzing a large software ecosystem to detect
software bugs. For our research we used
{\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10,SHP06}.
Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the
{\it Maven Central Repository}\footnote{\url{http://mvnrepository.com/}}
(approximately 265{\sc gb} of data.

@@

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.38]{figures/bug_percent}
	\caption{Bug percentage in Maven repository.}
	\label{fig:bug-per} 
\end{figure}

@@

\bibliographystyle{abbrv}
\bibliography{msr}  
\end{document}
